In conclusion, can we consider this group project as a success?
\begin{subsection}{A Contract}
  The purpose of our third year group project is to build a proof of concept for cattle muzzle recognition. During the past four months, we have developed the following modular components:
  \begin{enumerate}
    \item A restfull API that is globally accessible
    \item A stateless mobile application for Android and iOS
    \item A stateless web application
    \item A prototype for 2D cattle muzzle recognition
    \item An scalable infrastruture to host the service
  \end{enumerate}
  Each of which corresponds to a distinct autonomous micro-service. When put together, they form a complete system which provides a farmer a tool with which he can register, manage, track and identify his cattle. As a proof of concept all of the components are suboptimal has there is room for improvement. However what we provide is a fully modular solution which can be updated
\end{subsection}

\begin{subsection}{A Learning Experience}
  The group project is first and formost a learning experience. Through it, we discovered and learned to use many tools as well refine other skills. The scope of our solution involves different languages and entails many software engineering challenges which are addressed with tools such as React, Redux, Cordova, AWS, etc. It was also great opportunity to apply the knowledge acquiered in different courses. Software Engineering Design helped us conceptualise our application. Software Engineering Practice helped us organize our work. Computer Vision help us build the actual recognition algorithm. Deep Learning acted as a taught experiment to what could be possibly done in the future. In addition, it was a preparation for working in industry as gained and practiced skills sought after in the workplace. Work as a team on large scale projects. Deliver work on strict deadlines. Communicate and synchronize our vision of the platform with our client.
\end{subsection}
