%------------------------------------------------------------------------------
% Planning
%------------------------------------------------------------------------------

\subsection{Planning}

The CowHub project started with very open-ended objectives, as seen above. Clearly, focused and specific planning was required. For the first week of the project we sought to narrow down exactly what this project meant and hoped to achieve, and the resulting week-long sprint proved highly successful and we realised the following:

\begin{itemize}
	\item We needed to delegate our responsibilities, between front-end interfaces and for back-end services
	\item The pivot point in our project would be a central, open API which would provide the backbone between our public and private services
	\item We needed to use stable, durable systems with sufficient amounts of compute power available, and link these with a solid continuous integration and deployment system
\end{itemize}

%------------------------------------------------------------------------------
% Group organisation
%------------------------------------------------------------------------------

\subsection{Group Organisation}

In the beginning, the group members allocated each other responsibilities, according to the above:

\begin{itemize}
	\item	\textbf{Frederick Lindsey} \\
		  	Initial web front-end and basic API gateway, providing stateless session management, and performant asynchronous access to back-end services. Lead team direction on back-end services and infrastructure.
		  	Bootstrapping the web front-end and API gateway repositories, and setting up continuous integration and deployment.
	\item 	\textbf{Thomas Szyszko} \\
		  	Investigated and implemented a portable mobile platform which could be used to input cattle information and identify cattle.
		  	
	\item 	\textbf{Hongjiang Liu} \\
	 	  	Researched and implemented an algorithm to process an image into keypoints used for comparison to provide functionality determining how similar images and their textures are.
	\item	\textbf{Karim Nahas} \\
			Extending the API gateway and mobile platform to provide a comprehensive solution offering complex functionality.
	\item	\textbf{Gregoire Yharrassarry} \\
			
			
\end{itemize}

As the project progressed, the responsibilities we each had became more and more general and translated across the platform. The group became very adaptable as the depth of each member's knowledge grew and we could all pick up any task on most components. The group had great flexibility when different members time constraints changed and was able to maintain a constant level of progress throughout the project resulting in a project that has been consistently worked on for three months. Crucial to this was meeting on a regular basis and maintaining persistent communication largely in the form of online communication and note-taking.

%------------------------------------------------------------------------------
% Breakdown and task allocation
%------------------------------------------------------------------------------

\subsection{Breakdown and Task Allocation}

During the course of the project, the group experienced a myriad of changes to the way in which we managed ourselves and the tools we used. This allowed us to continually improve our productivity potential, although it did cause issues for our overall progress.

\subsubsection{Tracking todos}



\subsubsection{Communication}







